Vv explore

### 2023-02-12 code/analysis_code/exploratory_vv.qmd
Minor edits

All sites
```{r}
all<- vv %>% 
  mutate(site = recode(site, "BO" = "Blind Oso",
                              "C2" = "Canals",
                              "RD" = "Gulf")) %>%
  ggplot() + geom_line(
    aes(x = date,
        y = copies_mL,
        color = site)) + 
  scale_color_manual( values = c("Blind Oso" = "darkgreen",
                                "Canals" = "darkred",
                                "Gulf" = "darkblue"))+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date", 
    y = "Copies/mL",
    title = "Vibrio vulnificus Levels Across Dust Time Series: Trial 1")+
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5))

all
```
All Redo
```{r}
all_redo<- redo %>% 
  mutate(site = recode(site, "BO" = "Blind Oso",
                              "C2" = "Canals",
                              "RD" = "Gulf")) %>%
  ggplot() + geom_line(
    aes(x = date,
        y = copies_mL,
        color = site)) + 
  scale_color_manual( values = c("Blind Oso" = "darkgreen",
                                "Canals" = "darkred",
                                "Gulf" = "darkblue"))+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date", 
    y = "Copies/mL",
    title = "Vibrio vulnificus Levels Across Dust Time Series: Trial 2")+
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5))

@@

>>>>

All sites
```{r}
all<- vv %>% 
  mutate(site = recode(site, "BO" = "Blind Oso",
                              "C2" = "Canals",
                              "RD" = "Gulf")) %>%
  ggplot() + geom_line(
    aes(x = date,
        y = copies_mL,
        color = site)) + 
  scale_color_manual( values = c("Blind Oso" = "darkgreen",
                                "Canals" = "darkred",
                                "Gulf" = "darkblue"))+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date", 
    y = "Copies/mL",
    title = "Vibrio vulnificus Levels Across Dust Time Series: Trial 1")+
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5),
    axis.text.y = element_text(size = 15))

all
```
All Redo
```{r}
all_redo<- redo %>% 
  mutate(site = recode(site, "BO" = "Blind Oso",
                              "C2" = "Canals",
                              "RD" = "Gulf")) %>%
  ggplot() + geom_line(
    aes(x = date,
        y = copies_mL,
        color = site)) + 
  scale_color_manual( values = c("Blind Oso" = "darkgreen",
                                "Canals" = "darkred",
                                "Gulf" = "darkblue"))+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date", 
    y = "Copies/mL",
    title = "Vibrio vulnificus Levels Across Dust Time Series: Trial 2")+
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5),
    axis.text.y = element_text(size = 15))

@@

Compare Trial 1 and 2
```{r, fig.height=7, fig.width=7}
figure2<- ggarrange(all, all_redo,
                    ncol = 1, nrow = 2)
figure2
```
